Comunicações Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-05-06 tese/section01.tex
corrected some minor syntax errors

Jitsi Meet\footnote{\url{http://jitsi.org/Projects/JitsiMeet}} is a \ac{WebRTC} collaborative application that uses Jitsi Videobridge for high quality and scalable video conferences and supports shared document editing. Jitsi Videobridge is a server that enables multiparty video calls.

>>>>

\textit{Jitsi Meet}\footnote{\url{http://jitsi.org/Projects/JitsiMeet}} is a \ac{WebRTC} collaborative application that uses \textit{Jitsi Videobridge} for high quality and scalable video conferences and supports shared document editing. \textit{Jitsi Videobridge} is a server that enables multi-party video calls.

### 2015-05-06 tese/section02.tex
corrected some minor syntax errors

  One of signaling requisites is bi-directional communication over \ac{HTTP}. \ac{HTTP} works on a request followed by a server response, by other words, follows a unidirectional communication. Sometimes it's required that some informations are obtained in real time, as we saw, some \ac{NAT}'s don't suport callbacks from servers, one technique to overcome this problem is polling.

>>>>

  One of signaling requisites is bi-directional communication over \ac{HTTP}. \ac{HTTP} works on a request followed by a server response, by other words, follows a unidirectional communication. Sometimes it's required that some informations are obtained in real time, as we saw, some \ac{NAT}'s don't support callbacks from servers, one technique to overcome this problem is polling.

### 2015-05-06 tese/section03.tex
corrected some minor syntax errors

  \item \textbf{Animation} module contains elements and attributes that define a time based mechanism for composing the effects of animations. For example, this module can changes on \ac{XML} or \ac{CSS} attributes like colour and dimensions.

@@

  \item \textbf{Layout} module contains elements and attributes for colouring and positioning media content, another layout mechanisms are also possible, such as \ac{CSS}.

@@

  \item \textbf{Media Object} module contains elements and attributes for referencing rendering behaviour of external multimedia or control objects.

>>>>

  \item \textbf{Animation} module contains elements and attributes that define a time based mechanism for composing the effects of animations. For example, this module can changes on \ac{XML} or \ac{CSS} attributes like color and dimensions.

@@

  \item \textbf{Layout} module contains elements and attributes for coloring and positioning media content, another layout mechanisms are also possible, such as \ac{CSS}.

@@

  \item \textbf{Media Object} module contains elements and attributes for referencing rendering behavior of external multimedia or control objects.
